### 2019-03-28 report/chapter03.Rnw
Update 28.03

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

<<echo=FALSE>>=
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'thesis/code')
source(file.path(PATH, 'prepare.R'))

@@

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "linreg")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
\label{egger.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "mm")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
\label{thomson.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "rank")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
\label{begg.cont}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
\label{peters.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
\label{harbord.bin}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
trimfill.cont <- yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2))$k0 / n())

@@

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
trimfill.bin <- yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())

>>>>

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.5, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

<<echo=FALSE>>=
# PATH_HOME = path.expand("~") # user home
# PATH = file.path(PATH_HOME, 'thesis/code')
# source(file.path(PATH, 'prepare.R'))

PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH, 'code')
PATH_RESULTS = file.path(PATH, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

file_results = "pb.RData"

source(file.path(PATH_CODE, 'PubBias_functions.R'))

data = pb.readData(path = PATH_DATA, file = FILE)
tmp = pb.clean(data)
data = tmp[[1]]
aliases = tmp[[2]]

@@

\begin{figure}
<<echo=FALSE>>=
data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "linreg")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
\label{egger.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "mm")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
\label{thomson.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "rank")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
\label{begg.cont}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
\label{peters.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
\label{harbord.bin}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
trimfill.cont <- data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2))$k0 / n())

@@

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())
